---
title: "Comparison of First-name Popularity Across Districts of Berlin"
author: "Graham Booth"
date: "10/25/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
The following analysis compares the frequency of selected first names across the various districts of Berlin. It was created using RMarkdown and Plotly and uses a dataset that can be found on the Berlin Open Data website [here](https://daten.berlin.de/datensaetze/liste-der-häufigen-vornamen-2020) and is free to share and adapt under the following [creative commons license](https://creativecommons.org/licenses/by/3.0/de/).

The two chosen names are displayed on an interactive radar chart, which can be hovered over, zoomed-in on or selected to better understand the data. The names themselves can be changed by editing them within the RMarkdown file itself and re-knitting the html file. See the relevant lines [here](https://github.com/sidechained/DDP-Assignment-Week-3/blob/main/ddp_plotly.Rmd#L43).

```{r, echo=FALSE, message=FALSE}
library(dplyr)
base_path = "https://github.com/berlinonline/haeufige-vornamen-berlin/raw/master/data/cleaned/2020/"
filenames = c(
  "charlottenburg-wilmersdorf.csv",
  "friedrichshain-kreuzberg.csv",
  "lichtenberg.csv",
  "marzahn-hellersdorf.csv",
  "mitte.csv",
  "neukoelln.csv",
  "pankow.csv",
  "reinickendorf.csv",
  "spandau.csv",
  "steglitz-zehlendorf.csv",
  "tempelhof-schoeneberg.csv",
  "treptow-koepenick.csv"
)
masterframe <- data.frame()
for (filename in filenames) {
  if (!file.exists(filename)) { download.file(paste0(base_path, filename), filename) }
  thisframe <- read.csv(filename) %>% mutate(district = substr(filename,1,nchar(filename)-4))
  masterframe <- bind_rows(masterframe, thisframe)
}
summedframe <- masterframe %>% group_by(district, vorname) %>% summarize(anzahl = sum(anzahl))

# Produce a radar chart in plotly, based on two names from dataset
name1 <- "Marie"
name2 <- "Anna"
name1frame <- summedframe %>% filter(vorname == name1)
name2frame <- summedframe %>% filter(vorname == name2)

library(plotly)
fig <- plot_ly(
    type = 'scatterpolar',
    fill = 'toself'
  ) 
fig <- fig %>%
  add_trace(
    r = name1frame %>% pull(anzahl),
    theta = name1frame %>% pull(district),
    name = name1
  ) 
fig <- fig %>%
  add_trace(
    r = name2frame %>% pull(anzahl),
    theta = name2frame %>% pull(district),
    name = name2
  ) 
fig <- fig %>%
  layout(
    polar = list(
      radialaxis = list(
        visible = T,
        range = c(0,summedframe %>% pull(anzahl) %>% max())
      )
    )
  )
fig
```